Through the eyes of the teacher

### 2021-03-17 paper_1/paper_1_supplement_et_gri.tex
update plots GRI

\hypertarget{questionnaire-data}{%
\subsubsection{Questionnaire data}\label{questionnaire-data}}

After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior (students n = 24). In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).

\hypertarget{behavioral-data}{%
\subsubsection{Behavioral data}\label{behavioral-data}}

The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

@@

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes.
The scales on the quality of teaching are a validated questionnaire (Helmke et al., 2014). Whereas the scales on the teacher's presence behavior were derived from the research literature (Brophy, 1986; Kiel, Frey, Weiß, \& Weiss, 2013; Kounin, 2006; Marzano, 2007; Nolting, 2012) and were used in the pilot for the first time. The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree). Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).

The following scales were assessed:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
\item
  Positive climate and motivation
\item
  Clarity and structuredness
\item
  Activation and support
\item
  Presence: posture/gaze
\item
  Presence: voice
\item
  Presence: verbal and non-verbal intervention
\item
  Natural behaviour
\end{enumerate}

Table \ref{tab:table-all-scales-self-assessment} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the teachers' self-assessment.

\begin{verbatim}
## Some items ( ks_sichtbar ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\caption{\label{tab:table-all-scales-self-assessment}Scale analysis for teachers' self-assessment}

\begin{tabular}{lllllllll}
\toprule
scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
\midrule
Activation and support & 3 & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
Clarity and structuredness & 2 & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
Classroom management & 4 & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
Natural behaviour & 3 & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
Positive climate and motivation & 6 & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
Presence: posture/gaze & 7 & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
Presence: verbal and non-verbal intervention & 3 & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
Presence: voice & 3 & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
\bottomrule
\end{tabular}

Table \ref{tab:table-all-scales-students} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the students' perception of the teacher's behaviour in class.

\begin{verbatim}
## Some items ( phb_stand ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( pi_direkt ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( phb_stand ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\caption{\label{tab:table-all-scales-students}Scale analysis for students' perspective}

\begin{tabular}{lllllllll}
\toprule
scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
\midrule
Activation and support & 3 & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
Clarity and structuredness & 2 & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
Classroom management & 4 & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
Natural behaviour & 3 & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
Positive climate and motivation & 6 & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
Presence: posture/gaze & 7 & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
Presence: verbal and non-verbal intervention & 3 & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
Presence: voice & 3 & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
\bottomrule
\end{tabular}

The individual items of a scale are further represented in graphs.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Line Plots Classroom Management-1.pdf}
  \newpage
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Positive climate and motivation line plots-1.pdf}
  \newpage
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Clarity and structuredness line plots-1.pdf}
  \newpage
\item
  Activation and support
  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Activation and support line plots-1.pdf}
  \newpage
\end{enumerate}

{\centering \includegraphics[width=5.33in]{./pictures/presenceposturegaze}

\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
\end{figure}

{\centering \includegraphics[width=5.33in]{./pictures/presencevoice}

\caption{(6) Presence: voice}\label{fig:presencevoice}
\end{figure}
\newpage

{\centering \includegraphics[width=5.33in]{./pictures/presenceverbalnonverbalintervention}

\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
\end{figure}
\newpage

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Natural behaviour line plots-1.pdf}
  \newpage
  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
\end{enumerate}

\begin{figure}
\centering
\includegraphics{paper_1_supplement_new_table_files/figure-latex/boxplot scales-1.pdf}
\caption{(\#fig:boxplot scales)Boxplots and individual data for experts and novices}
\end{figure}

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz \& Rädiker, 2019). The following coding scheme was developed:

\begin{itemize}
\item
  phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
\item
  phase - lesson end, state event: teacher finishes the lesson with a noise, talk, taking a position in class
\item
  phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working material, organizing desks, opening windows, printing work results etc.)
\item
  phase - single, state event: any individual student activity on a given task (reading, writing, drawing etc.)
\item
  phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
\item
  phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
\item
  phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
\item
  phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board, OHP etc.
\item
  phase - other, state event: not categorizable
\item
  phase - break, state event: e.g.~drinking, relaxation exercises
\item
  phase - external interruption, state event: external interruptions (e.g.~fire alarm, technical problems, other teachers coming into the room)
\item
  speaking time - teacher, state event
\item
  speaking time - students, state event
\item
  disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\item
  disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
\end{itemize}

First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher. The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.

\includegraphics{paper_1_supplement_new_table_files/figure-latex/speaking plot-1.pdf}

@@

@@

\caption{\label{tab:GRItable}Number and Duration (in msec) of Fixations}

\begin{tabular}{lllllll}
\toprule
Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
\midrule
01\_01\_D & Expert & 803.00 & 316,571.00 & 394.00 & 781,978.00 & 0.49\\
01\_02\_A & Expert & 1,070.00 & 385,812.00 & 361.00 & 838,026.00 & 0.34\\
01\_03\_B & Novice & 617.00 & 374,315.00 & 607.00 & 744,444.00 & 0.98\\
01\_04\_C & Novice & 769.00 & 384,537.00 & 500.00 & 723,922.00 & 0.65\\
02\_01\_A & Novice & 569.00 & 101,541.00 & 178.00 & 729,762.00 & 0.31\\
02\_02\_B & Novice & 1,140.00 & 520,431.00 & 457.00 & 730,565.00 & 0.40\\
02\_03\_C & Novice & 1,048.00 & 469,018.00 & 448.00 & 737,604.00 & 0.43\\
02\_04\_D & Novice & 613.00 & 438,655.00 & 716.00 & 747,729.00 & 1.17\\
\bottomrule
\end{tabular}

@@

\caption{\label{tab:Disturbance "head on table" to first intervention}Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention}

\begin{tabular}{lllllll}
\toprule
Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
\midrule
01\_01\_D & Expert & 3.00 & 2,079.00 & 693.00 & 5,735.00 & 231.00\\
01\_02\_A & Expert & 7.00 & 2,778.00 & 397.00 & 8,454.00 & 56.71\\
01\_03\_B & Novice & 1.00 & 460.00 & 460.00 & 3,493.00 & 460.00\\
01\_04\_C & Novice & 29.00 & 12,653.00 & 436.00 & 16,245.00 & 15.03\\
\bottomrule
\end{tabular}

@@

\hypertarget{questionnaire-data-2}{%
\subsubsection{Questionnaire Data}\label{questionnaire-data-2}}

\hypertarget{behavioral-data-2}{%
\subsubsection{Behavioral Data}\label{behavioral-data-2}}

@@

\hypertarget{questionnaire-data-3}{%
\subsubsection{Questionnaire Data}\label{questionnaire-data-3}}

\hypertarget{behavioral-data-3}{%
\subsubsection{Behavioral Data}\label{behavioral-data-3}}

@@

\leavevmode\hypertarget{ref-brophy1986classroom}{}%
Brophy, J. (1986). Classroom management techniques. \emph{Education and Urban Society}, \emph{18}(2), 182--194.

@@

\leavevmode\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}%
Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M. (2014). Unterrichtsdiagnostik mit EMU. \emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.

@@

\leavevmode\hypertarget{ref-kiel2013trainingsbuch}{}%
Kiel, E., Frey, A., Weiß, S., \& Weiss, S. (2013). \emph{Trainingsbuch klassenf{ü}hrung} (Vol. 3992). UTB.

@@

\leavevmode\hypertarget{ref-kounin2006techniken}{}%
Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.

\leavevmode\hypertarget{ref-kuckartz2019analyzing}{}%
Kuckartz, U., \& Rädiker, S. (2019). \emph{Analyzing qualitative data with MAXQDA}. Springer.

@@

\leavevmode\hypertarget{ref-marzano2007art}{}%
Marzano, R. J. (2007). \emph{The art and science of teaching: A comprehensive framework for effective instruction}. Ascd.

@@

\leavevmode\hypertarget{ref-nolting2012storungen}{}%
Nolting, H.-P. (2012). \emph{St{ö}rungen in der schulklasse}. Beltz.

>>>>

@@

@@

The first table provides an overview over the

@@

\caption{\label{tab:GRItable1}GRI}

\begin{tabular}{lllllllll}
\toprule
TOI & \multicolumn{1}{c}{ID} & \multicolumn{1}{c}{Group} & \multicolumn{1}{c}{DurTOI} & \multicolumn{1}{c}{M Dur Fix} & \multicolumn{1}{c}{Number Fix} & \multicolumn{1}{c}{TimeTOI Dur} & \multicolumn{1}{c}{OldGRI} & \multicolumn{1}{c}{NewGRI}\\
\midrule
Asking question & 01\_04\_C & Novice & 3,869.00 & 2,925.62 & 3.00 & 1.32 & 975.21 & 0.44\\
Asking question & 01\_02\_A & Expert & 7,112.00 & 2,925.62 & 13.00 & 2.43 & 225.05 & 0.19\\
Asking question & 01\_03\_B & Novice & 12,863.00 & 2,925.62 & 4.00 & 4.40 & 731.41 & 1.10\\
Asking question & 01\_01\_D & Expert & 7,648.00 & 2,925.62 & 7.00 & 2.61 & 417.95 & 0.37\\
Asking question & 02\_01\_A & Novice & 7,422.00 & 2,925.62 & 3.00 & 2.54 & 975.21 & 0.85\\
Asking question & 02\_02\_B & Novice & 7,082.00 & 2,925.62 & 9.00 & 2.42 & 325.07 & 0.27\\
Asking question & 02\_03\_C & Novice & 8,045.00 & 2,925.62 & 8.00 & 2.75 & 365.70 & 0.34\\
Asking question & 02\_04\_D & Novice & 6,595.00 & 2,925.62 & 6.00 & 2.25 & 487.60 & 0.38\\
Calibration phase & 01\_04\_C & Novice & 17,224.00 & 12,275.12 & 14.00 & 1.40 & 876.79 & 0.10\\
Calibration phase & 01\_02\_A & Expert & 13,335.00 & 12,275.12 & 10.00 & 1.09 & 1,227.51 & 0.11\\
Calibration phase & 01\_03\_B & Novice & 10,615.00 & 12,275.12 & 17.00 & 0.86 & 722.07 & 0.05\\
Calibration phase & 01\_01\_D & Expert & 16,470.00 & 12,275.12 & 9.00 & 1.34 & 1,363.90 & 0.15\\
Calibration phase & 02\_01\_A & Novice & 17,902.00 & 12,275.12 & 13.00 & 1.46 & 944.24 & 0.11\\
Calibration phase & 02\_02\_B & Novice & 12,325.00 & 12,275.12 & 12.00 & 1.00 & 1,022.93 & 0.08\\
Calibration phase & 02\_03\_C & Novice & 16,494.00 & 12,275.12 & 18.00 & 1.34 & 681.95 & 0.07\\
Calibration phase & 02\_04\_D & Novice & 20,964.00 & 12,275.12 & 14.00 & 1.71 & 876.79 & 0.12\\
Chatting with neighbour & 01\_04\_C & Novice & 9,843.00 & 4,070.12 & 27.00 & 2.42 & 150.75 & 0.09\\
Chatting with neighbour & 01\_02\_A & Expert & 2,607.00 & 4,070.12 & 1.00 & 0.64 & 4,070.12 & 0.64\\
Chatting with neighbour & 01\_03\_B & Novice & 11,060.00 & 4,070.12 & 10.00 & 2.72 & 407.01 & 0.27\\
Chatting with neighbour & 01\_01\_D & Expert & 6,612.00 & 4,070.12 & 3.00 & 1.62 & 1,356.71 & 0.54\\
Chatting with neighbour & 02\_01\_A & Novice & 7,429.00 & 4,070.12 & 5.00 & 1.83 & 814.02 & 0.37\\
Chatting with neighbour & 02\_02\_B & Novice & 8,397.00 & 4,070.12 & 11.00 & 2.06 & 370.01 & 0.19\\
Chatting with neighbour & 02\_03\_C & Novice & 11,713.00 & 4,070.12 & 11.00 & 2.88 & 370.01 & 0.26\\
Chatting with neighbour & 02\_04\_D & Novice & 11,443.00 & 4,070.12 & 4.00 & 2.81 & 1,017.53 & 0.70\\
Clicking pen & 01\_04\_C & Novice & 12,980.00 & 8,809.75 & 4.00 & 1.47 & 2,202.44 & 0.37\\
Clicking pen & 01\_02\_A & Expert & 12,071.00 & 8,809.75 & 20.00 & 1.37 & 440.49 & 0.07\\
Clicking pen & 01\_03\_B & Novice & 26,272.00 & 8,809.75 & 16.00 & 2.98 & 550.61 & 0.19\\
Clicking pen & 01\_01\_D & Expert & 11,597.00 & 8,809.75 & 11.00 & 1.32 & 800.89 & 0.12\\
Clicking pen & 02\_01\_A & Novice & 16,114.00 & 8,809.75 & 11.00 & 1.83 & 800.89 & 0.17\\
Clicking pen & 02\_02\_B & Novice & 9,409.00 & 8,809.75 & 12.00 & 1.07 & 734.15 & 0.09\\
Clicking pen & 02\_03\_C & Novice & 16,269.00 & 8,809.75 & 27.00 & 1.85 & 326.29 & 0.07\\
Clicking pen & 02\_04\_D & Novice & 24,220.00 & 8,809.75 & 19.00 & 2.75 & 463.67 & 0.14\\
Drawing on paper & 01\_04\_C & Novice & 39,979.00 & 34,414.38 & 27.00 & 1.16 & 1,274.61 & 0.04\\
Drawing on paper & 01\_02\_A & Expert & 44,971.00 & 34,414.38 & 87.00 & 1.31 & 395.57 & 0.02\\
Drawing on paper & 01\_03\_B & Novice & 129,708.00 & 34,414.38 & 79.00 & 3.77 & 435.62 & 0.05\\
Drawing on paper & 01\_01\_D & Expert & 74,511.00 & 34,414.38 & 92.00 & 2.17 & 374.07 & 0.02\\
Drawing on paper & 02\_01\_A & Novice & 43,469.00 & 34,414.38 & 31.00 & 1.26 & 1,110.14 & 0.04\\
Drawing on paper & 02\_02\_B & Novice & 147,788.00 & 34,414.38 & 295.00 & 4.29 & 116.66 & 0.01\\
Drawing on paper & 02\_03\_C & Novice & 26,495.00 & 34,414.38 & 46.00 & 0.77 & 748.14 & 0.02\\
Drawing on paper & 02\_04\_D & Novice & 27,915.00 & 34,414.38 & 11.00 & 0.81 & 3,128.58 & 0.07\\
Drumming hands & 01\_04\_C & Novice & 43,507.00 & 11,415.88 & 41.00 & 3.81 & 278.44 & 0.09\\
Drumming hands & 01\_02\_A & Expert & 20,530.00 & 11,415.88 & 27.00 & 1.80 & 422.81 & 0.07\\
Drumming hands & 01\_03\_B & Novice & 12,615.00 & 11,415.88 & 6.00 & 1.11 & 1,902.65 & 0.18\\
Drumming hands & 01\_01\_D & Expert & 23,121.00 & 11,415.88 & 17.00 & 2.03 & 671.52 & 0.12\\
Drumming hands & 02\_01\_A & Novice & 62,326.00 & 11,415.88 & 50.00 & 5.46 & 228.32 & 0.11\\
Drumming hands & 02\_02\_B & Novice & 24,699.00 & 11,415.88 & 25.00 & 2.16 & 456.64 & 0.09\\
Drumming hands & 02\_03\_C & Novice & 27,775.00 & 11,415.88 & 49.00 & 2.43 & 232.98 & 0.05\\
Drumming hands & 02\_04\_D & Novice & 14,998.00 & 11,415.88 & 9.00 & 1.31 & 1,268.43 & 0.15\\
Looking at phone & 01\_04\_C & Novice & 7,984.00 & 11,563.00 & 8.00 & 0.69 & 1,445.38 & 0.09\\
Looking at phone & 01\_02\_A & Expert & 19,897.00 & 11,563.00 & 28.00 & 1.72 & 412.96 & 0.06\\
Looking at phone & 01\_03\_B & Novice & 40,427.00 & 11,563.00 & 30.00 & 3.50 & 385.43 & 0.12\\
Looking at phone & 01\_01\_D & Expert & 32,387.00 & 11,563.00 & 29.00 & 2.80 & 398.72 & 0.10\\
Looking at phone & 02\_01\_A & Novice & 33,557.00 & 11,563.00 & 14.00 & 2.90 & 825.93 & 0.21\\
Looking at phone & 02\_02\_B & Novice & 16,321.00 & 11,563.00 & 19.00 & 1.41 & 608.58 & 0.07\\
Looking at phone & 02\_03\_C & Novice & 28,223.00 & 11,563.00 & 47.00 & 2.44 & 246.02 & 0.05\\
Looking at phone & 02\_04\_D & Novice & 31,944.00 & 11,563.00 & 19.00 & 2.76 & 608.58 & 0.15\\
Putting head on table & 01\_04\_C & Novice & 20,929.00 & 17,049.88 & 38.00 & 1.23 & 448.68 & 0.03\\
Putting head on table & 01\_02\_A & Expert & 23,402.00 & 17,049.88 & 27.00 & 1.37 & 631.48 & 0.05\\
Putting head on table & 01\_03\_B & Novice & 39,159.00 & 17,049.88 & 41.00 & 2.30 & 415.85 & 0.06\\
Putting head on table & 01\_01\_D & Expert & 6,354.00 & 17,049.88 & 4.00 & 0.37 & 4,262.47 & 0.09\\
Putting head on table & 02\_01\_A & Novice & 51,225.00 & 17,049.88 & 45.00 & 3.00 & 378.89 & 0.07\\
Putting head on table & 02\_02\_B & Novice & 11,322.00 & 17,049.88 & 20.00 & 0.66 & 852.49 & 0.03\\
Putting head on table & 02\_03\_C & Novice & 61,713.00 & 17,049.88 & 81.00 & 3.62 & 210.49 & 0.04\\
Putting head on table & 02\_04\_D & Novice & 57,484.00 & 17,049.88 & 42.00 & 3.37 & 405.95 & 0.08\\
Yelling & 01\_04\_C & Novice & 6,083.00 & 889.50 & 1.00 & 6.84 & 889.50 & 6.84\\
Yelling & 01\_02\_A & Expert & 1,995.00 & 889.50 & 1.00 & 2.24 & 889.50 & 2.24\\
Yelling & 01\_03\_B & Novice & 6,527.00 & 889.50 & 1.00 & 7.34 & 889.50 & 7.34\\
Yelling & 01\_01\_D & Expert & 2,245.00 & 889.50 & 1.00 & 2.52 & 889.50 & 2.52\\
Yelling & 02\_01\_A & Novice & 9,105.00 & 889.50 & 7.00 & 10.24 & 127.07 & 1.46\\
Yelling & 02\_02\_B & Novice & 2,548.00 & 889.50 & 5.00 & 2.86 & 177.90 & 0.57\\
Yelling & 02\_03\_C & Novice & 2,992.00 & 889.50 & 2.00 & 3.36 & 444.75 & 1.68\\
Yelling & 02\_04\_D & Novice & 12,416.00 & 889.50 & 1.00 & 13.96 & 889.50 & 13.96\\
\bottomrule
\end{tabular}

\caption{\label{tab:GRItable2}GRI}

\begin{tabular}{lllllllll}
\toprule
Group & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
\midrule
Expert & Asking question & 2,108.50 & 10.00 & 7,380.00 & 231.70 & 98.30 & 0.39 & 0.18\\
Expert & Calibration phase & 12,283.00 & 9.50 & 14,902.50 & 1,296.54 & 96.50 & 0.13 & 0.03\\
Expert & Chatting with neighbour & 1,829.00 & 2.00 & 4,609.50 & 1,219.33 & 862.20 & 1.32 & 0.16\\
Expert & Clicking pen & 5,416.50 & 15.50 & 11,834.00 & 381.62 & 156.68 & 0.15 & 0.06\\
Expert & Drawing on paper & 25,514.50 & 89.50 & 59,741.00 & 285.30 & 11.27 & 0.03 & 0.01\\
Expert & Drumming hands & 8,405.00 & 22.00 & 21,825.50 & 402.85 & 129.48 & 0.13 & 0.05\\
Expert & Looking at phone & 8,484.50 & 28.50 & 26,142.00 & 297.79 & 7.39 & 0.11 & 0.03\\
Expert & Putting head on table & 7,605.50 & 15.50 & 14,878.00 & 1,091.53 & 1,145.29 & 0.16 & 0.07\\
Expert & Yelling & 580.00 & 1.00 & 2,120.00 & 580.00 & 0.00 & 3.66 & 0.30\\
Novice & Asking question & 3,198.00 & 5.50 & 7,646.00 & 703.26 & 320.81 & 0.51 & 0.30\\
Novice & Calibration phase & 12,272.50 & 14.67 & 15,920.67 & 853.95 & 130.15 & 0.09 & 0.03\\
Novice & Chatting with neighbour & 4,817.17 & 11.33 & 9,980.83 & 617.28 & 384.64 & 0.26 & 0.18\\
Novice & Clicking pen & 9,940.83 & 14.83 & 17,544.00 & 955.00 & 774.90 & 0.15 & 0.09\\
Novice & Drawing on paper & 37,381.00 & 81.50 & 69,225.67 & 1,233.52 & 1,156.72 & 0.04 & 0.02\\
Novice & Drumming hands & 12,419.50 & 30.00 & 30,986.67 & 791.90 & 760.35 & 0.10 & 0.04\\
Novice & Looking at phone & 12,589.17 & 22.83 & 26,409.33 & 747.59 & 459.89 & 0.10 & 0.05\\
Novice & Putting head on table & 20,198.00 & 44.50 & 40,305.33 & 535.53 & 252.70 & 0.04 & 0.02\\
Novice & Yelling & 992.67 & 2.83 & 6,611.83 & 635.78 & 409.08 & 4.76 & 4.60\\
\bottomrule
\end{tabular}

\caption{\label{tab:GRItable3}GRI}

\begin{tabular}{llllllll}
\toprule
Group & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
\midrule
Expert & 8,025.17 & 21.50 & 18,159.17 & 1,953.05 & 2,871.09 & 0.16 & 0.08\\
Novice & 12,645.43 & 25.33 & 24,958.93 & 1,878.32 & 2,902.64 & 0.13 & 0.15\\
\bottomrule
\end{tabular}

@@

@@

\hypertarget{questionnaire-data}{%
\subsubsection{Questionnaire Data}\label{questionnaire-data}}

\hypertarget{behavioral-data}{%
\subsubsection{Behavioral Data}\label{behavioral-data}}

@@

@@

@@

@@

@@

@@

@@
